My english activity log

### 2019-10-06 english-activity.Rmd
29/09
jusque 02/10
jusque 06/10

29/09/2019 : I found other Youtube channels : Bleier Biology, Biology Bugbears, Bozeman science, Amoeba sisters, Free science lessons, Biomedical and Biological sciences.

.

>>>>

29/09/2019 : I found other Youtube channels : Bleier Biology, Biology Bugbears, Bozeman science, Amoeba sisters, Free science lessons, Biomedical and Biological sciences.
I read the first chapter of "The Hobbit"

02/10/2019 : I read the wikipedia article about cockatiel for my Data Science homework.

05/10/2019 : I read some articles for my presentation and I watched a video about diffusion (https://www.youtube.com/watch?v=jhszFBtBPoI)

06/10/2019 : I read some articles for my presentation, I read the second chapter of "The Hobbit" and I watched a vide about cell cycle (https://www.youtube.com/watch?v=QVCjdNxJreE)
